Unsupervised embedding of trajectories captures the latent structure of mobility

### 2020-10-20 paper/current/main.tex
change to legal name

\subsection*{Korean accommodation reservation data}
We source Korean accommodation reservation data from collaboration with Good Choice Company in Korea, containing 938,962 trajectories spanning the time period of August 2018 through July 2020,  comprising 1,038 unique accommodation locations in Seoul, South Korea.

>>>>

\subsection*{Korean accommodation reservation data}
We source Korean accommodation reservation data from collaboration with Goodchoice Company LTD. in Korea, containing 938,962 trajectories spanning the time period of August 2018 through July 2020,  comprising 1,038 unique accommodation locations in Seoul, South Korea.
